The function-sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-25 crelle-dictionary.tex
Abstract under construction

\begin{abstract}
By extending the scope of function-sheaf dictionary for connected commutative algebraic groups, we find a geometrization of characters of all smooth commutative group schemes over finite fields.
As an application, we explain how to geometrize and categorify quasicharacters of all connected commutative algebraic groups over non-Archimedean local fields that admit a locally finite type Neron model, such as algebraic tori, abelian varieties and unipotent K-wound groups.
\end{abstract}

@@

\begin{proof}
 Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
 Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
 Then $\qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
 $b_G^* \qcs{E}$ comes equipped with an isomorphism
 $\phi_\qcs{E} : \Frob{G}^* b_G^*\qcs{E} \to b_G^* \qcs{E}$.
 The functor $\qcs{E} \mapsto (b_G^* \qcs{E},\phi_\qcs{E})$
 from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
 is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
 This functor preserves local constancy, so takes local systems to local systems.
 The isomorphism $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$ satisfies \ref{QC.2}
 with $b_G^*\qcs{E}$ playing the role of $\gqcs{L}$.
 Moreover, $\phi_\qcs{E}$ is compatible with $\mu_\qcs{E}$ in the sense of \ref{QC.3}.
 This construction defines the functor $B_G : (\qcs{E},\mu_\qcs{E}) \mapsto (b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E}, \phi_\qcs{E})$
 and also shows that it is full and faithful.
\end{proof}

>>>>

\begin{abstract}
We extend the function-sheaf dictionary to smooth commutative group schemes over finite fields. 
As an application, we explain how to geometrize and categorify quasicharacters of  algebraic tori, abelian varieties and unipotent K-wound groups over connected commutative algebraic groups over non-Archimedean local fields that admit a Neron model locally of finite type,
\end{abstract}

@@

\begin{proof}
 Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
 Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
 Then $\qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
 $b_G^* \qcs{E}$ comes equipped with an isomorphism
 $\phi_\qcs{E} : \Frob{G}^* b_G^*\qcs{E} \to b_G^* \qcs{E}$.
 The functor $\qcs{E} \mapsto (b_G^* \qcs{E},\phi_\qcs{E})$
 from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
 is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
 This functor preserves local constancy, so takes local systems to local systems.
 The isomorphism $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$ satisfies \ref{QC.2}
 with $b_G^*\qcs{E}$ playing the role of $\gqcs{L}$.
 Moreover, $\phi_\qcs{E}$ is compatible with $\mu_\qcs{E}$ in the sense of \ref{QC.3}.
 This construction defines the functor $B_G : (\qcs{E},\mu_\qcs{E}) \mapsto (b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E}, \phi_\qcs{E})$
 and also shows that it is full and faithful.
\end{proof}
